\documentclass[12pt,onesided,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[none]{hyphenat}
\usepackage{xcolor}
\usepackage[pdfnewwindow=true]{hyperref}
\hypersetup{colorlinks=false,linkbordercolor=red,linkcolor=green,pdfborderstyle={/S/U/W 1}}

\pagestyle{empty}
\setlength\parindent{0pt}

\begin{document}
\section*{Code of Conduct}

All attendees, speakers, sponsors and volunteers at GunnHacks are required to agree with the following code of conduct. Organizers will enforce this code throughout the event. We are expecting cooperation from all participants to help ensure a safe environment for everybody.

\subsection*{The Quick Version}

GunnHacks is dedicated to providing a harassment-free experience for everyone, regardless of gender, sexual orientation, disability, physical appearance, body size, race, or religion. We do not tolerate harassment of GunnHacks participants in any form. Sexual language and imagery is not appropriate for any GunnHacks venue, including talks, workshops, parties, Twitter and other online media. GunnHacks participants violating these rules may be sanctioned or expelled from GunnHacks at the discretion of the organizers.

\subsection*{The Less Quick Version}

Harassment includes offensive verbal comments related to gender, sexual orientation, disability, physical appearance, body size, race, religion, sexual images in public spaces, deliberate intimidation, stalking, following, harassing photography or recording, sustained disruption of talks or other events, inappropriate physical contact, and unwelcome sexual attention.  Participants asked to stop any harassing behavior are expected to comply immediately.\\

Sponsors are also subject to the anti-harassment policy. In particular, sponsors should not use sexualized images, activities, or other material. Staff (including volunteers) should not use sexualized clothing/uniforms/costumes, or otherwise create a sexualized environment.\\

If a participant engages in harassing behavior, GunnHacks organizers may take any action they deem appropriate, including warning the offender or immediate expulsion from the event.\\

If you are being harassed, notice that someone else is being harassed, or have any other concerns, please contact a member of conference staff immediately. A member of the GunnHacks staff will be on site throughout the hackathon.\\

GunnHacks staff will be happy to help participants contact security or local law enforcement, provide escorts, or otherwise assist those experiencing harassment to feel safe for the duration of the conference. We value your attendance.\\

We expect participants to follow these rules at GunnHacks and GunnHacks-related social events. 

\section*{Useful Information}

Gunn High School has wireless access available. Connect to the StudentWireless network with the password ``studentwireless''.\\

There are bathrooms outside rooms N-115 and N-215. Drinking fountains are also located just outside the classrooms.\\

THERE IS NO EATING FOOD IN THE CLASSROOMS. Please eat outside of the classroom.\\

There are compost, recycle, and trash bins outside of the classrooms, too.  Here are the rules:
\begin{itemize}
\item If it contains foil, or if it is a plastic that does not have a recycle symbol, it goes in the trash bin.
\item If it was once alive (animal, vegetable---includes trees) it goes in the compost.
\item If it was never alive, recycle.  Plastic bottles and aluminum cans will be the most common examples.
\end{itemize}

There will be designated rooms on the second floor of the N building for rest. Please be respectful of others by keeping as quiet as reasonably possible in those rooms.\\

When it comes to evaluating projects for prizes, the decision of the judges is final.\\

If you have any administrative questions during the event, please ask Josh Paley or other Gunn teachers who will be wearing black and red lambda-thing guy T-shirts and baseball caps.

\section*{Credits}
Original source and credit:\\
\href{http://redmonk.com/thingmonk/code-of-conduct/}{http://redmonk.com/thingmonk/code-of-conduct/}\\
\href{http://2012.jsconf.us/#/about}{http://2012.jsconf.us/\#/about}\\
\& The Ada Initiative\\

This particular source and credit: \href{https://www.eclipsecon.org/na2015/code-conduct}{https://www.eclipsecon.org/na2015/code-conduct}\\

Please help by translating or improving: \href{http://github.com/leftlogic/confcodeofconduct.com}{http://github.com/leftlogic/confcodeofconduct.com}\\

This work is licensed under a Creative Commons Attribution 3.0 Unported License.

\end{document}
