\documentclass[12pt,onesided,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[none]{hyphenat}
\usepackage{xcolor}
\usepackage[pdfnewwindow=true]{hyperref}
\hypersetup{colorlinks=false,linkbordercolor=red,linkcolor=green,pdfborderstyle={/S/U/W 1}}
\usepackage{fontspec}
\newfontfamily\DejaSans{DejaVu Sans}

\pagestyle{empty}
\setlength\parindent{0pt}

\begin{document}
\section*{GunnHacks 2.0 Important Information}

GunnHacks 2.0 is this weekend! We're excited, and hope you are, too. Please take a look at the following document for logistical information that you should be aware of.

\subsection*{Venue \& Getting Here}

GunnHacks 2.0 will be at Henry M. Gunn High School at 780 Arastradero Rd, Palo Alto, CA 94306 in the N building. There will be GunnHacks volunteers in the parking lot guiding you to where you need to go. Also, see \href{https://gunnhacks.com/map.pdf}{the annotated campus map}.\\

Of note, if you plan on taking Caltrain, the closest station is Palo Alto's California Avenue, not University. Cal Ave is approximately a 30 minute walk to Gunn.\\

If you're driving, there will be afternoon traffic. Plan accordingly.\\

During the hackathon you can park in any of the main student lots for free without a permit. You cannot, however, park in the staff or otherwise reserved spots. There should be tons of space. Drop off is easiest from the back side\slash Miranda drop off.

\subsection*{Schedule}

GunnHacks 2.0 will run from 7 pm Friday, March 25 to 7 pm Saturday, March 26.\\

Check-in for hackers starts at 6:30 pm. You will need to have your current student ID or other equivalent as well as the signed photo\slash media release form. You will be expected to sign the GunnHacks Code of Conduct at registration.\\

The updated schedule can be found on \href{https://gunnhacks.com}{our website}. We will have tons of fun events and workshops throughout the hackathon.

\subsection*{Waivers}

You have already read and agreed to \href{http://static.mlh.io/docs/mlh-code-of-conduct.pdf}{the MLH Code of Conduct and Data Sharing Provision} during registration. You will also need to read \href{https://gunnhacks.com/code.pdf}{the GunnHacks Code of Conduct}, which you will be asked to sign for during registration. You also need to sign and bring a completed \href{https://gunnhacks.com/waiver.pdf}{photo\slash media release} with both your and your parent's signatures (if you're a minor).

\subsection*{In-and-Out Privileges}

You will be allowed to leave and enter as you wish, as long as you check in with the registration desk.

\subsection*{Communication}

We will be sending out a couple of emails during the event, so make sure you check your spam and ``Promotions''.\\

On top of that, we will be using Slack. You should have received an invite on Thursday. If you did not, you can get one from \href{https://slack.gunnhacks.com}{our slackin}.\\

You can also join \href{https://www.facebook.com/events/1706103592980386/}{our Facebook event} and follow us on \href{https://www.facebook.com/GunnHacks}{Facebook} and \href{https://twitter.com/GunnHacks}{Twitter} for updates.

\subsection*{Mentors}

We will have some amazing mentors at the event! You can ask them for help through the \#mentors channel on Slack, and they will be walking around during the duration of the hackathon.

\subsection*{Things You Might Want To Bring}

\begin{itemize}
\item Student ID\slash equivalent identification
\item Signed waiver with parent (for minors) and student signatures
\item Laptop, phone
\item Chargers
\item Sleeping bag
\item Toiletries
\item Change of clothes
\end{itemize}

\subsection*{Food}

We will not be serving dinner on either Friday or Saturday. Eat before you come or enjoy the light refreshments and snacks. Breakfast and lunch on Saturday will be provided free of charge.\\

If you have a reusable water bottle, bring it! We'll have bottled water, but help us preserve the environment by filling up from the water fountains instead.

\subsection*{Network}

There will be WiFi at the event. Hackers do not have access to Ethernet. If you have any large software downloads to do, please do them ahead of arriving at the event. The Internet connection at Gunn cannot accommodate 100 hackers downloading software at once. {\DejaSans 😛}

\subsection*{Project Submissions}

Demo sign ups will open at 2 pm on Saturday. Demos will begin at approximately 4:30 pm. Spectators (e.g. parents) are welcome to come see the demos.

\subsection*{Hardware}

We have some awesome hardware to lend out to hackers during the event, courtesy of Major League Hacking. In order to check out hardware, you'll need a credit\slash debit card or passport. We will return these items to you upon return of the hardware. Don't worry---we won't charge your card.\\

10x Intel Edison\\
6x Arduino\\
6x Arduino Uno\\
6x Arduino 101\\
Assorted sensors, buttons and wires for Arduino and Intel Edison\\
3x Firephone\\
10x Leap\\
3x Muse\\
12x Oculus\\
20x Pebble\\
10x Sparkcore\\
24x Myo\\
3x Dell Monitors\\
2x Dell XPS Laptops\\
2x Dell Alienware Laptops\\
1x Nest

\subsection*{Final Notes}

We want this to be a fun event for everyone. To that end, if you have any concerns about your safety or that of others, or have an immediate emergency concern during the event, reach out to a GunnHacks organizer, or contact (650) 814-9700.

Also, please consider donating to the event. The suggested donation is \$10, although we will happily accept anything you can contribute. While GunnHacks is completely free, your support encourages the continuing success of the event for future years! You are under no obligation or expectation to donate. Your donation is tax-deductible.\\

If for some reason, you are unable to attend, please let us know! There is a waiting list and we want to accommodate as many people as possible.\\

If you have any questions or concerns, feel free to reach out to us at info@gunnhacks.com.\\

See you Friday!

\end{document}
